---
title: "Lab 00 - Hello IDS!"
author: "Leuxan Huang"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Lexuan Huang"),
  github_username = c("luciahuanglx-png"), 
  colour = c("blue"),
  hobby = c("shopping"),
  favourite_number = c(6)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

The plot shows each team member's favourite number, with their GitHub username on the x-axis and their favourite number on the y-axis. The colour of each bar represents their favourite colour. Since I am working individually, the plot contains one blue bar showing my favourite number, 6.

